---
title: 'Work Sheet #2'
author: "Jonathan Cary Sucaldito"
date: "2025-09-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Exercise 1 Create a vector using : operator
a. Sequence from -5 to 5. Write the R code and its output. Describe its output.
```{r setup, include=FALSE}
y <- c(-5:5)
print(y)
```
output: it's out put is sequential from -5 to 5
 [1] -5 -4 -3 -2 -1  0  1  2  3  4  5
b. x <- 1:7. What will be the value of x?
```{r setup, include=FALSE}
x <- c(1:7)
print(x)
```
The value of x is:
[1] 1 2 3 4 5 6 7

##Exercise 2.* Create a vector using seq() function
a. seq(1, 3, by=0.2) # specify step size
Write the R code and its output. Describe the output.
```{r setup, include=FALSE}
vec <- seq(1, 3, by = 0.2)
print(vec)
```
the output is sequential by 0.2
 [1] 1.0 1.2 1.4 1.6 1.8 2.0 2.2 2.4 2.6 2.8 3.0
 
##Exercise A factory has a census of its workers. There are 50 workers in total. 
The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

a. Access 3rd element, what is the value?
```{r setup, include=FALSE}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
ages

ages[3]
```
the value is: [1] 22

b. Access 2nd and 4th element, what are the values?
```{r setup, include=FALSE}
ages[c(2,4)]
```
the value of the outputs are
[1] 28 36


c. Access all but the 1st element is not included. Write the R code and its output.
```{r setup, include=FLASE}
ages[2:50]
```
the output is:
[1] 28 22 36 27 18 52 39 42 29 35 31 27 22 37 34 19 20 57 49 50 37 46 25 17 37 43 53 41 51 35 24 33 41 53 40 18
[37] 44 38 41 48 27 39 19 30 61 54 58 26 18

##4. *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).
```{r setup, include=FALSE}
x <- c("first" = 3, "second" = 0, "third" = 9)
```
a. Print the results. Then access x[c("first", "third")]. Describe the output.
```{r setup, include=FALSE}
print(x)
x[c("first", "second")]
```
the output is:
 first second 
     3      0 
b. Write the code and its output.
```{r setup, include=FALSE}
x[c("first", "second")]
# first second 
#     3      0 
```

##Exercise 5. Create a sequence x from -3:2.
```{r setup, include=FALSE}
x <- c(-3:2)
print(x)
```
a. Modify 2nd element and change it to 0;
x[2] <- 0
x
Describe the output.
```{r setup, include=FALSE}
x[2] <- 0
x
```
the output is: 
[1] -3  0 -1  0  1  2

b. Write the code and its output.
```{r setup, include=FALSE}
x[2] <- 0
x
#[1] -3  0 -1  0  1  2
```

