---
title: 'Work Sheet #2'
author: "Jonathan Cary Sucaldito"
date: "2025-09-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Exercise 1 Create a vector using : operator
a. Sequence from -5 to 5. Write the R code and its output. Describe its output.
```{r setup, include=FALSE}
y <- c(-5:5)
print(y)
```
output: it's out put is sequential from -5 to 5
 [1] -5 -4 -3 -2 -1  0  1  2  3  4  5
b. x <- 1:7. What will be the value of x?
```{r setup, include=FALSE}
x <- c(1:7)
print(x)
```
The value of x is:
[1] 1 2 3 4 5 6 7

##Exercise 2.* Create a vector using seq() function
a. seq(1, 3, by=0.2) # specify step size
Write the R code and its output. Describe the output.
```{r setup, include=FALSE}
vec <- seq(1, 3, by = 0.2)
print(vec)
```
the output is sequential by 0.2
 [1] 1.0 1.2 1.4 1.6 1.8 2.0 2.2 2.4 2.6 2.8 3.0
 
##Exercise A factory has a census of its workers. There are 50 workers in total. 
The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

a. Access 3rd element, what is the value?
```